Results

### 2024-08-14 scripts/Results.Rmd
content

scouting <- left_join(scouting, files, by = c('taxa' = 'species')) |>
  mutate(Presence = if_else(POPULATION_SIZE > 0, 1, 0), .after = POPULATION_SIZE)

@@

suitability_amounts <- readRDS('../data/processed/prcntSDMsurfaceSuitable.rds')
suitability_amounts <- bind_rows(suitability_amounts)

suitability_means <- suitability_amounts |>
  group_by(Percent) |>
  summarise(Mean = mean(Records))

par(pty="s")
plot(suitability_means$Mean, suitability_means$Percent, type = "l", col = "red", 
     ylab = "% of all Raster Cells", xlab = "Cumulative Sum of Records at each Predicted Suitability")

ggplot(suitability_amounts, aes(Percent, Records, color = Species, group = Species)) +
  geom_line() +
  scale_color_grey(guide = 'none') + 
  geom_line(data = suitability_means, 
            aes(Percent, Mean), inherit.aes = F, color = '#093824', lwd = 1) + 
  labs(
    y = "% of all Raster Cells",
    x = 'Cumulative sum of records at each quantile of Predicted Suitability') + 
  theme_classic() +
  theme(aspect.ratio = 1/1)

'#292E1E'
'#1F271B'
'#003E1F'
'#003E1F'
'#093824'
'#04471C'
'#1F2F16'
'#137547'
'#2A9134'

'#254441'
'#395B50'
'#73BA9B'
'#519872'

rm(files)
```

@@

fp <- scout1[scouting$futurePotential=='Yes',]

quants <- quantile(fp$suitability, na.rm = TRUE, probs = c(0.25, 0.5, 0.75))
hist(fp$suitability)
abline(v = quants[[1]], lwd = 2)
abline(v = quants[[2]], lwd = 2)
abline(v = quants[[3]], lwd = 2)

@@

```{r}
quants
```

@@

```{r}
hist(fp$Rank)
```

>>>>

scouting <- left_join(scouting, files, by = c('taxa' = 'species')) |>
  mutate(Presence = if_else(POPULATION_SIZE > 0, 1, 0), .after = POPULATION_SIZE) |>

  # penstemon palmeri are all seeded outside their native range and 'helped' along
  # during establishment we will remove them from the analysis

  filter(taxa != 'Penstemon_palmeri')

@@

suitability_amounts <- readRDS('../data/processed/prcntSDMsurfaceSuitable.rds')
suitability_amounts <- bind_rows(suitability_amounts)
remotes::install_github("bcgov/elucidate")

y1 <- rnorm(1:10, 100, 10)
elucidate::mean_ci(y1)

recs <- filter(suitability_amounts, Percent == 50) |>
  pull(Records)

as.numeric( elucidate::mean_ci(recs, replicates = 1000, ci_level = 0.99) )

prctn <- split(suitability_amounts, f = suitability_amounts$Percent)
suitability_means <- lapply(prctn, \(x)
  data.frame(as.list(
    elucidate::mean_ci(x$Records, replicates = 1000, ci_level = 0.99))
  )
) |>
  bind_rows() |>
  mutate(Percent = 1:100)

fp <- scouting[scouting$futurePotential=='Yes',] 
fp <- arrange(fp, suitability) |>
  st_drop_geometry() |>
  select(suitability) |>
  mutate(obs = 1:n() / n())

linecols <- c(
  'Species' = 'grey50',
  "Mean" = "#093824", 
  "95% CI" = "#73BA9B",
  "Populations" = "#FF2C55"
  )

ggplot(suitability_amounts, aes(x = Percent, y = Records, color = Species, group = Species)) +
  geom_line(lty = 1) +
  scale_color_grey(guide = 'none') + 
  geom_ribbon(data = suitability_means, aes(ymin = lower, ymax = upper, x = Percent),
              fill = '#73BA9B', inherit.aes = F, alpha = 0.5) + 
  geom_line(data = suitability_means, 
            aes(x = Percent, y =  mean, color = 'a'), color = '#093824', inherit.aes = F, lwd = 1) + 
  geom_line(data = fp, aes(x = suitability*100, y = obs), color = '#FF2C55', inherit.aes = F,  lwd = 1)

  labs(
    title = 'Populations are found in\nareas with higher suitability',
    x = "Raster Cells (cumulative)",
    y = 'Predicted Suitability (cumulative)') + 
  theme_classic() +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), sec.axis = sec_axis(~.*100,
    name = 'Populations Found (cumulative)',
    breaks = seq(0, 100, by = 20), 
    labels = \(x) paste0(x, "%"))
  )  +

  scale_x_continuous(breaks = seq(0, 100, by = 20), labels = \(x) paste0(x, "%")) + 
  theme(
    plot.title = element_text(hjust = 0.5),
    aspect.ratio = 1/1)

rm(linecols)

hypothetical_curves
```

@@

fp <- scouting[scouting$futurePotential=='Yes',] 
quants <- quantile(fp$suitability, na.rm = TRUE, probs = c(0.25, 0.5, 0.75))

hist(fp$suitability)
abline(v = quants[[1]], lwd = 2)
abline(v = quants[[2]], lwd = 2)

@@

@@

- can we test moving the distance patches into their own categories ??? 
```{r}
hist(fp$Rank)
```
